---
title: "Chhota-Bheem-Doraemon-Dragon-Tales"
author: "Khushboo"
df_print: paged
---

### ***Chhota Bheem vs Doraemon vs Dragon Tale***\~

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(broom)
library(crosstable)
library(knitr)
library(kableExtra)
library(supernova)
library(ggprism)
library(patchwork)
library(infer)
library(jtools)
library(flextable)

```

Let's first import and read our data set.

```{r}
cartoon <- read_csv("C:/Users/khush/Downloads/cartoon.csv")
cartoon
```

```{r}
glimpse(cartoon)
```

## Data Munging

```{r}
cartoon2 <- cartoon %>% 
  mutate(
    Gender = as_factor(Gender),
    Cartoon = as_factor(Cartoon)
  )
glimpse(cartoon)
```

#### *NULL Hypothesis for this data set?*\~

```{r}
# Calculate mean and standard deviation of Rating
summary_stats <- cartoon %>%
  summarize(
    Mean_Rating = mean(Rating, na.rm = TRUE),
    SD_Rating = sd(Rating, na.rm = TRUE)
  )

# Print the summary statistics
print(summary_stats)


```

#### *Histogram*\~

```{r}
ggplot(cartoon, aes(x = Rating)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Ratings",
       x = "Rating",
       y = "Frequency") +
  theme_minimal()

```

```{r}
unique(cartoon$Gender)

```

#### *ANOVA*\~

```{r}
cartoon_anova <- aov(Rating ~ Cartoon, data = cartoon2)
cartoon_anova
```

#### *Check for Normality*\~

```{r}
shapiro.test(x = cartoon2$Rating)
```

```{r}
cartoon2 %>%
  group_by(Cartoon) %>%
  group_modify(~ .x %>%
    select(Rating) %>%
    as_vector() %>%
    shapiro.test() %>%
    broom::tidy())
```

```{r}
cartoon2 %>%
  as_tibble() %>%
  gf_dhistogram(~Rating, data = .) %>%
  gf_fitdistr()
```

The ratings appear to be spread across with several peaks, indicating that the data may not follow a simple normal distribution..

#### *Permutation Test*\~

```{r}
observed_infer <- cartoon2 %>%
  specify(Rating ~ Cartoon) %>%
  hypothesise(null = "independence") %>%
  calculate(stat = "F")
observed_infer
```

The F-stat of 0.9 suggests that there is little to no difference in the means of the ratings of cartoons being compared.

After this, we perform the permutation test.

```{r}
null_dist_infer <- cartoon2 %>%
  specify(Rating ~ Cartoon) %>%
  hypothesise(null = "independence") %>%
  generate(reps = 4999, type = "permute") %>%
  calculate(stat = "F")
##
null_dist_infer
```

This null distribution allows us to evaluate the stance of the F-stat value. By comparing the observed F-stat to this null distribution, we can assess how unusual or extreme it is.

The distribution across all 4,999 samples show the overall spread of F-values under the null hypothesis.

```{r}
##
null_dist_infer %>%
  visualise(method = "simulation") +
  shade_p_value(obs_stat = observed_infer$stat, direction = "right") +
  scale_x_continuous(trans = "log10", expand = c(0, 0)) +
  coord_cartesian(xlim = c(0.2, 500), clip = "off") +
  annotation_logticks(outside = FALSE) 
```
