---
title: "Groups, class 5"
author: "Khushboo"
---

## Groups

I will be dealing with a new code and a new kind of plotting called gf_box plot and box plot respectively.

```{r}
library(tidyverse)
library(mosaic)
library(ggformula)
library(palmerpenguins)
library(skimr)
library(dplyr)
```

## Wages data set

```{r}
wages <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/stevedata/gss_wages.csv")
wages
```
```{r}
wages_clean <-
  wages %>%
  tidyr::drop_na(realrinc) # choose column or leave blank to choose all
```







```{r}
wages_clean %>%
  gf_boxplot(gender ~ realrinc) %>%
  gf_labs(title = "Plot 2A: Income by Gender")


```


```{r}
glimpse(wages)
```

```{r}
skim(wages)
```

```{r}
inspect(wages)
```

we note that this is a large dataset (61K rows), with 11 variables

```{r}
gf_boxplot(realrinc ~ 1, data = wages_clean) %>%
  gf_labs(
    title = "Plot 1A: Income has a skewed distribution",
    subtitle = "Many outliers on the high side"
  )

```

```{r}
wages_clean <-
  wages %>%
  tidyr::drop_na(realrinc)
```

### What is the basic distribution of realrinc?

```{r}
wages_clean %>%
  gf_boxplot(realrinc ~ "Income") %>% # Dummy X-axis "variable"
  gf_labs(
    title = "Plot 1A: Income has a skewed distribution",
    subtitle = "Many outliers on the high side"
  )
```

-   Business insights-

-   Income is a very skewed distribution, as might be expected.

-   Presence of many higher-side outliers is noted, going up

    ### is realrinc affected by gender?

    ```{r}
    wages_clean %>%
      gf_boxplot(gender ~ realrinc) %>%
      gf_labs(title = "Plot 2A: Income by Gender")
    ```

#### split by gender-

```{r}
wages_clean %>%
  gf_boxplot(gender ~ log10(realrinc)) %>%
  gf_labs(title = "Plot 2B: Log(Income) by Gender")
```

#### with log income-

```{r}
wages_clean %>%
  gf_boxplot(gender ~ realrinc, fill = ~gender) %>%
  gf_refine(scale_x_log10()) %>%
  gf_labs(title = "Plot 2C: Income filled by Gender, log scale")
```

## Is realrinc affected by education?

```{r}
wages_clean %>%
  gf_boxplot(educcat ~ realrinc) %>%
  gf_labs(title = "Plot 3A: Income by Education Category")
```

