---
title: "CoursesA3"
author: "Khushboo"
---

#### *Loading packages*\~

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(broom)
library(crosstable)
library(knitr)
library(kableExtra)
library(supernova)
library(ggprism)
library(patchwork)
library(infer)
library(jtools)
library(flextable)
library(tidyr)
library(ggplot2)
library(perm)
library(coin)

```

#### *Importing dataset*\~

```{r}
courses <- read_csv("../../Data/courses.csv")
courses
```

```{r}
glimpse(courses)
```

```{r}
inspect(courses)
```

```{r}
skim(courses)
```

#### *Data munging*\~

```{r}

data <- read.table(header = TRUE, text = "
SN Degree Course Year Letter_Grade Score Gender
1 B.Des CAC 2 A 8 F
2 B.Des CAC 2 O 9.6 F
3 B.Des IADP 2 A+ 9.2 F
4 B.Des CE 2 O 9.8 F
5 B.Des BSSD 2 P 3 M
6 B.Des CAC 2 O 9.5 F
7 B.Des PSD 2 A+ 9 F
8 B.Des PSD 2 A+ 9 F
9 B.Des PSD 2 A+ 9 F
10 B.Des BSSD 3 A+ 9 F
11 B.Des VCSB 2 A 8 F
12 B.Des VCSB 2 A 8 F
13 B.Des IAIDP 3 A 8 M
14 B.Des IAIDP 3 B+ 7 M
15 B.Des VCSB 2 B+ 7 F
16 B.Des HCD 3 A+ 9 M
17 B.Des CAC 3 A+ 9.1 F
18 B.Des VCSB 2 A 8 M
19 B.Des CE 2 A+ 9 F
20 B.Des CAC 2 A+ 9 M
21 B.Des IADP 2 A 8 F
22 B.Des IADP 3 B+ 7 M
23 B.Des VCSB 3 A+ 9 F
24 B.Des CE 2 O 10 F
25 B.Des CAC 3 A+ 9 F
26 B.Des CAC 3 A+ 9 F
27 B.Des PSD 3 B+ 7 F
28 B.Des PSD 3 A 8 F
29 B.Des CAC 2 A+ 9 F
30 B.Des HCD 2 A 8 F
31 B.Voc UIID 3 O 9.5 F
32 B.Voc UIID 3 A+ 9 F
33 B.Voc UIID 3 A+ 9 M
34 B.Voc UIID 3 B+ 7 M
35 B.Voc UIID 3 A 8 F
36 B.Voc UIID 3 A 8 F
37 B.Voc ID 3 B+ 7 M
38 B.Voc DMP 3 O 9.5 M
39 B.Voc DMP 3 B 6.5 M
40 B.Voc DMP 3 O 9.5 M
41 B.Voc DMP 3 O 9.5 M
42 B.Voc DMP 3 A+ 9 M
43 B.Voc DMP 3 O 9.5 F
44 B.Voc DMP 3 O 9.5 F
45 B.Voc DMP 3 B 6.5 F
46 B.Voc DMP 3 C 5 M
47 B.Voc UIID 1 A+ 9 M
48 B.Voc UIID 1 B 7 F
49 B.Voc UIID 1 B 7 F
50 B.Voc UIID 1 A 8 F
51 B.Voc UIID 1 A 8 F
52 B.Voc UIID 1 A+ 9 F
53 B.Voc UIID 2 A 8 M
54 B.Voc GADP 1 A 8 F
55 B.Voc GADP 2 A 8 M
56 B.Voc Film 3 A 8 M
57 B.Voc GADP 3 A+ 9 F
58 B.Voc GADP 3 A+ 9 F
59 B.Voc DMP 2 A 8 M
60 B.Voc DMP 2 A 8 M
61 B.FA CAP 3 A 8 F
62 B.FA CAP 3 A+ 9 M
63 B.FA CAP 3 A+ 9 F
64 B.FA DMA 2 A+ 8.5 M
65 B.FA DMA 2 A 8 M
66 B.FA DMA 2 A 8 F
67 B.FA CAP 2 A 8 F
68 B.FA CAP 2 A+ 8 F
69 B.FA Film 3 B 6 M
70 B.FA DMA 2 A 8 F
71 B.FA DMA 2 B+ 7 F
72 B.FA DMA 2 B+ 7 F
73 B.FA DMA 2 A 8 F
74 B.FA DMA 2 B+ 7 F
75 B.FA DMA 2 B 6 M
76 B.FA Film 3 A 8 M
77 B.FA Film 3 A 8 M
78 B.FA DMA 2 A 8 M
79 B.FA DMA 2 A 8 M
80 B.FA DMA 2 B+ 7 F
81 B.FA DMA 2 B+ 7 F
82 B.FA Film 2 A 8 F
83 B.FA Film 3 B+ 7 F
84 B.FA DMA 2 A+ 9 F
85 B.FA DMA 2 A 8 M
86 B.FA DMA 2 B+ 7 F
87 B.FA DMA 2 B+ 7 F
88 B.FA DMA 2 B+ 7 M
89 B.FA DMA 2 B+ 7 F
90 B.FA DMA 2 B+ 7 F
")

# Ensure Score is numeric
data$Score <- as.numeric(data$Score)

```

#### *Calculating mean and standard deviation*\~

```{r}
mean_score <- mean(data$Score, na.rm = TRUE)
sd_score <- sd(data$Score, na.rm = TRUE)

# Null hypothesis
null_hypothesis <- "H0: Mean Score = 7"

mean_score
sd_score
null_hypothesis

```

-   **Mean Score:** 8.068.068.06

-   **Standard Deviation:** 1.131.131.13

-   **Null Hypothesis (H0):** "Mean Score = 7"

### Inferences and Conclusions:

1.  **Mean Score Interpretation:**

    -   The mean score of approximately 8.068.068.06 suggests that, on average, students in this dataset are performing above the hypothetical mean of 777 specified in the null hypothesis. This indicates generally good academic performance.

2.  **Standard Deviation Interpretation:**

    -   The standard deviation of 1.131.131.13 indicates that there is some variability in student scores, but it is not excessively high. This means that while most scores are relatively close to the mean (between approximately 6.936.936.93 and 9.199.199.19 if we consider one standard deviation from the mean), there are some differences in student performance.

3.  **Comparison to Null Hypothesis:**

    -   Since the mean score (8.068.068.06) is greater than the mean specified in the null hypothesis (777), preliminary analysis suggests that students, on average, perform significantly better than the baseline.

#### *Graph*\~

```{r}
# Histogram of Scores
ggplot(data, aes(x = Score)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "white") +
  theme_minimal() +
  labs(title = "Histogram of Scores", x = "Score", y = "Frequency")

# Boxplot of Scores by Gender
ggplot(data, aes(x = Gender, y = Score)) +
  geom_boxplot(fill = "lightblue") +
  theme_minimal() +
  labs(title = "Boxplot of Scores by Gender", x = "Gender", y = "Score")

```

#### *ANOVA*\~

```{r}
# Perform ANOVA
anova_results <- aov(Score ~ Gender, data = data)
summary(anova_results)

# Bonferroni Post-hoc test
posthoc_results <- pairwise.t.test(data$Score, data$Gender, p.adjust.method = "bonferroni")
posthoc_results

```

```{r}
shapiro_test <- shapiro.test(data$Score)
shapiro_test

```

-   **Null Hypothesis (H0):** The null hypothesis of the Shapiro-Wilk test states that the data is normally distributed.

-   **Interpretation of the p-value:**

    -   The p-value is extremely small (9.198×10−79.198 \\times\^{-7}9.198×10−7), which is much lower than the common alpha level of 0.050.050.05.

    -   This indicates strong evidence against the null hypothesis.

-   **Conclusion:**

    -   Since the p-value is less than 0.05, you reject the null hypothesis. This suggests that the scores in your dataset are **not normally distributed**.

    -   The low W statistic further supports this conclusion, as values closer to 111 indicate a stronger adherence to normality.

```{r}
anova_results <- aov(Score ~ Gender, data = data)
summary(anova_results)
```



-   **Null Hypothesis (H0):** The null hypothesis states that there is no difference in mean scores between genders (i.e., the true mean difference is zero).

-   **Interpretation of the p-value:**

    -   The p-value of 0.064450.064450.06445 is slightly above the common significance level of 0.050.050.05.

    -   This suggests that there is not enough evidence to reject the null hypothesis at the 0.050.050.05 significance level.

    #### *Summary*\~

    In summary, while the data indicates generally strong student performance, the analyses underscore the importance of recognizing variability in achievement and the need for further examination of potential differences in performance by gender. Further research could provide deeper insights and lead to targeted educational strategies to enhance overall student success.
