---
title: "A3pocketmoney"
author: "Khushboo"
---

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(broom)
library(crosstable)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
```

```{r}
Pocket_Money <- read_csv("../../Data/Pocket Money.csv")
Pocket_Money
```

```{r}
glimpse(Pocket_Money)
```

```{r}
inspect(Pocket_Money)
```

```{r}
skim(Pocket_Money)
```

```{r}
Pocket_Money2 <- Pocket_Money %>%
    mutate(
        Preferance = case_when(
            Money_spent > 500 ~ "High Spender",
            Money_spent > 200 & Money_spent <= 500 ~ "Medium Spender",
            TRUE ~ "Low Spender"
        )
    )

# Convert 'Preferance' to a factor
Pocket_Money2 <- Pocket_Money2 %>%
    mutate(
        Preferance = as_factor(Preferance)
    )

glimpse(Pocket_Money2)
```

#### *Mean and standard deviation*\~

```{r}
# Calculate mean of Money_spent
Pocket_Money_mean <- mean(Pocket_Money$Money_spent)

# Calculate standard deviation of Money_spent
Pocket_Money_sd <- sd(Pocket_Money$Money_spent)

cat("Mean money spent:", Pocket_Money_mean, "\n")
cat("Standard deviation of money spent:", Pocket_Money_sd)
```

#### *Histograms for the dataset*\~

```{r}
ggplot(Pocket_Money, aes(x = Money_spent)) + 
  geom_histogram(fill = "lightblue", color = "black") + 
  labs(title = "Histogram of Money Spent", x = "Money Spent", y = "Frequency")
```

```{r}
plot(density(Pocket_Money$Money_spent), 
     main = "Density Plot of Money Spent", 
     xlab = "Money Spent", 
     ylab = "Density")
```

```{r}
hist(Pocket_Money$Money_spent)
```

### *What is our null hypothesis?*

-   There is no significant difference in the average amount of money spent between male and female individuals.

-   This hypothesis suggests that any observed difference in the mean spending between the two genders is due to random chance and not a true difference in the population.

### *Checking for Normality*\~

#### *Wilcox test*\~

```{r}
shapiro.test(Pocket_Money$Money_spent)
```

#### *t-test*\~

```{r}

male_spending <- Pocket_Money$Money_spent[Pocket_Money$Gender == "Male"]
female_spending <- Pocket_Money$Money_spent[Pocket_Money$Gender == "Female"]

t_test_result <- t.test(male_spending, female_spending)

print(t_test_result)
```

```{r}
shapiro.test(Pocket_Money$Money_spent)
```

#### Permutation:

```{r}
Pocket_Money <- Pocket_Money %>%
  mutate(Preferance = ifelse(Money_spent > 200, "High Spender", "Low Spender"))
```

```{r}

# Create a Preferance variable based on a threshold (e.g., high spenders vs. low spenders)
Pocket_Money2 <- Pocket_Money2 %>%
  mutate(Preferance = ifelse(Money_spent > 200, "High Spender", "Low Spender"))

# Calculate the mean Money_spent for each Preferance group
group_means <- Pocket_Money2 %>%
  group_by(Preferance) %>%
  summarize(mean_Money_spent = mean(Money_spent))

# Calculate the difference in means
obs_diff_mean <- group_means$mean_Money_spent[1] - group_means$mean_Money_spent[2]

print(obs_diff_mean)
```

```{r}
Pocket_Money2 <- Pocket_Money2 %>%
  mutate(Preferance = ifelse(Money_spent > 200, "High Spender", "Low Spender"))

# Calculate the observed difference in means
observed_diff <- mean(Pocket_Money2$Money_spent[Pocket_Money2$Preferance == "High Spender"]) - 
                 mean(Pocket_Money2$Money_spent[Pocket_Money2$Preferance == "Low Spender"])

# Set the number of permutations
n_permutations <- 1000

permuted_diffs <- numeric(n_permutations)

for (i in 1:n_permutations) {
  permuted_data <- Pocket_Money2 %>%
    mutate(Preferance = sample(Preferance))
  
  permuted_diff <- mean(permuted_data$Money_spent[permuted_data$Preferance == "High Spender"]) - 
                   mean(permuted_data$Money_spent[permuted_data$Preferance == "Low Spender"])
  
  permuted_diffs[i] <- permuted_diff
}

# Plot the null distribution
hist(permuted_diffs, main = "Null Distribution of Difference in Means",
     xlab = "Difference in Means")
abline(v = observed_diff, col = "red") # Add a vertical line for the observed difference
```

```{r}

null_dist_df <- data.frame(Difference = permuted_diffs)

# Plot the null distribution with the observed difference
ggplot(null_dist_df, aes(x = Difference)) +
  geom_histogram(fill = "lightblue", color = "black", binwidth = 0.5, alpha = 0.8) +  # Adjust alpha for transparency
  geom_vline(xintercept = observed_diff, color = "red", linetype = "dashed", size = 1.2) +  # Adjust line thickness
  labs(title = "Null Distribution of Difference in Means",
       x = "Difference in Means",
       y = "Frequency") +
  theme_minimal()  
```
